%-------------------------------------------------------------------------------
% BOARD ENCODING
%-------------------------------------------------------------------------------
\subsection{Board encoding}
\begin{frame}{"Cogito" system overview}{Board encoding}

Each encountered state of the board is an object, while certain configurations 
deemed are attributes. A configuration is invariant with regards to translations 
and rotations.

\end{frame}

%-------------------------------------------------------------------------------
% EVALUATING CONFIGURATIONS
%-------------------------------------------------------------------------------
\subsection{Evaluating configurations}
\begin{frame}{"Cogito" system overview}{Evaluating configurations}

When the game ends the final configuration is given a value based on whether the 
agent has won or last. This value and is propagated backwards through previous
board states with linear attenuation. The value of a state board the value 
of its configurations.

\end{frame}

%-------------------------------------------------------------------------------
% GENERATING NEW CONFIGURATIONS
%-------------------------------------------------------------------------------
\subsection{Generating new configurations}
\begin{frame}{"Cogito" system overview}{Generating new configurations}

New relevant configurations are deduced by attempting to locally extend an 
existing configuration shared by two or more winning or losing board states.

\end{frame}

%-------------------------------------------------------------------------------
% PUTTING IT ALL TOGETHER
%-------------------------------------------------------------------------------
\subsection{Putting it all together}
\begin{frame}{"Cogito" system overview}{Putting it all together}

The system receives a set of possible moves to choose from. By evaluating each 
resulting board state based on prior experience it is able to choose the one 
which seems most beneficial.

Nota Bene: there is no look-ahead, but as we are essentially engineering a 
dynamic heuristic the system could be easily combined with a limited-depth 
Minimax implementation.

\end{frame}